---
title: "An Influx in Indian-American Baby Names?"
date: "MM/DD/YYYY"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
knit: (function(i, encoding) {apstyle::render(i, encoding)})
---

<!-- Timestamp: leave this in to automatically track when a file is rendered -->

*Rendered at `r format(Sys.time(), '%I:%M %p, %b. %d, %Y')`*

<!-- Contact info: leave author/reporter/editor contact info here -->

*Sherin Stanley ([sherinstanley\@gmail.com](mailto:sherinstanley@gmail.com){.email})*

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  )

knitr::opts_knit$set(
  root.dir = rprojroot::find_rstudio_root_file()
  )

```

```{r initialize}
# Load files, environment variables, libraries, etc. here
library(tidyverse)
library(apstyle)

natfilepaths <- list.files("~/Documents/babynames2023/data/source/names", full.names = TRUE)

nationaldf<-    map_df(natfilepaths,
                       function(x) {
                         read_csv(x, col_names = c("name","sex","babies")) %>%
                           mutate(year = as.numeric(
                             str_sub(x, nchar(x[1])-7,nchar(x[1])-4))
                           )
                       }
)
```

## Overview

### Was there an influx of Indian-American baby names during the 2000's Indian Immigration period?

  Imagine this. You're on a trip with your family and stop by at a souvenir store. You stumble across one of those personalized souvenir rotating carts, with any name you can think of - well, any American name you can think of. After hours of searching for your name, you find nothing. Or you might get lucky and settle for something that has some semblance to your own name, like a magnet with the name "Renee" on it, but your name isn't Renee. It's Renita. And after some contemplating on whether or not to buy the magnet, if that means losing your identity or if it's even that serious and it is just a magnet, you get it. 
  This is a common experience for many Indian American children growing up in the US. It has come to the point where many Indian Americans have started to choose more Americanized baby names for their kids. However, some parents are sticking with their original South Asian baby names to preserve their culture as much as they can. Another common experience Indian American children might experience is the relatability when they meet someone who shares the same name as them. To this day, I've never met anyone else named Sherin. The closest I've gotten to someone with the same name as me was a girl named Shirin who I met at a friend's birthday party in the fourth grade. 
  "That seems typical," is what one individual I interviewed, Jahnavi Alapati, said when looking at the graph below, "I don't know many Jahnavis, so it makes sense for my name to not show the same growth as the other names do." When asked if growing up with a more uncommon name had any effect on the way she looked at her identity growing up, she said that she dealt with many struggles dealing with her cultural identity. She often felt alienated by her peers and wished her name was something more common and not as "unique". However, growing up she realized that while we might deal with this sense of unbelonging, our parents faced much more trivial struggles for the sake of our futures. "Most of our parents are immigrants that only moved here in recent years. My mom's name is Arpita. She was probably one of the first Arpitas to even step foot in this country. But she's not complaining about the lack of Arpita's she's met in her life. She came to this country without even really knowing how to speak English, and had to learn how to navigate a new world all on her own. So while I might have wished I wasn't the only Jahnavi I knew growing up, I grew up in a predominately South Indian neighborhood, which helped me with my cultural identity in another much more impactful way thanks to my parents. They knew I would want to grow up around other people culturally similar to us, which is what they did."
  In a world where personalized souvenirs and relatability through names may seem trivial, the experiences of Indian American children reveal deeper struggles and the quest to preserve their cultural identity. The choice between Americanized and original South Asian names reflects the delicate balance between assimilation and heritage. While the lack of recognition can lead to a sense of alienation, the stories of individuals like Jahnavi Alapati shed light on the resilience of immigrant parents and the importance of community in shaping cultural identity. As the Indian American population continues to grow in numbers, the hope for increased acceptance and understanding of their names becomes ever more significant. Ultimately, this issue touches upon the complex interplay between individual identity, heritage, and the diverse fabric of American society.
  
    #talk about popularity of names/relatability, what did you find
    #why does it matter -> visibility matters
    #look at the variations of spelling, talk ab one thing being important and relating it to a larger trend
    #projection 
    #maya and mira also being common american names influencing the data??

```{r}
popular_today <- nationaldf %>%
  filter(year == 2022, name %in% c("Arjun", "Samir", "Aditya", "Nikhil", "Arnav","Jahnavi", "Maya", "Mira", "Anjali", "Shreya")) %>%
  arrange(desc(babies))
popular_today

```

```{r}
#The names I will be focusing on in my dataset are the following: Arjun, Samir, Aditya, Nikhil, Arnav, Jahnavi, Maya, Mira, Anjali, Shreya

#First I'll look at the boys names
boys_names <- nationaldf %>%
  group_by(year) %>%
  mutate(babies_max = max(babies)) %>%
  ungroup() %>%
  filter(name %in% c("Arjun", "Samir", "Aditya", "Nikhil", "Arnav"), 
         year >= 1950,
         sex == "M") %>%
  mutate(fraction_max = babies / babies_max)

ggplot(boys_names, aes(x = year, y = fraction_max, color = name)) +  geom_line() + scale_y_log10(labels=scales::label_percent()) + labs(title = "Popularity of These Indian Boy Names", caption = "Source: Social Security Administration", x = "Year", y = "%  of all Boy Babies", color = "Name") + theme_ap(family = "") + theme(legend.position = "right")
```

```{r}
#Now I'll look at the girls names
girls_names <-nationaldf %>%
  group_by(year) %>%
  mutate(babies_max = max(babies)) %>%
  ungroup() %>%
  filter(name %in% c("Jahnavi", "Maya", "Mira", "Deepika", "Priyanka"), 
         year >= 1950,
         sex == "F") %>%
  mutate(fraction_max = babies / babies_max)
ggplot(girls_names, aes(x = year, y = fraction_max, color = name)) +  geom_line() + scale_y_log10(labels=scales::label_percent()) + labs(title = "Popularity of These Indian Girl Names", x = "Year", y = "%  of all Girl Babies", caption = "Source: Social Security Administration") + theme_ap(family = "") + theme(legend.position = "right")
```

```{r}
jahnavi_analysis <- nationaldf %>%
  filter(name == "Jahnavi")
min_jahnavi <- which.min(jahnavi_analysis$babies)
jahnavi_analysis$year[min_jahnavi]
```

## References

<!-- This section is for including references to related material -->

-   CREDO National Charter School Study 2013: <http://credo.stanford.edu/documents/NCSS%202013%20Final%20Draft.pdf>

-   NBER Working Paper No. 23947: The Labor Market Effects of Offshoring by U.S. Multinational Firms: Evidence from Changes in Global Tax Policies: <http://www.nber.org/papers/w23947>

-   SSA Website: Beyond the Top 1000 Names: <https://www.ssa.gov/oact/babynames/limits.html>

-   Indian Immigrants in the United States: <https://www.migrationpolicy.org/article/indian-immigrants-united-states>

<!-- This section is for a tests code block -->

```{r tests}
# Leave this block of code at the end of the file
# If a test fails it will stop the Rmd document from knitting
# Run tests like so:
# source("tests/etl_test.R")
```
